The Effect of Elections and Changed Governments on Discussion in the Australian Federal Parliament (1901--2017)

### 2018-11-15 outputs/docs/events/paper.Rmd
Update paper

elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols())

top_words <- top_words %>% 
  rename(Topic = topic, Terms = terms)

@@

elections_results <- read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>% 
  # filter(Significant %in% c("Yes", "No"))
  filter(Significant %in% c("Yes"))

governments_results <- read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>% 
  filter(Significant %in% c("Yes")) %>% 
  # filter(Significant %in% c("Yes", "No")) %>% 
  select(-Party, -`Died in Office`)

key_events_results <- read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols())

@@

The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed text analysis of Canadian parliament records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada. A digitised version of the UK Hansard has been available for some time and there has been much text analysis of it. For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considers the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950. And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R, @R2018, to convert the PDFs into daily text records. An example of the workflow and some reduced-detail scripts are provided in Appendix \@ref(hansardworkflow). Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

@@

## Topic modelling
We applied the CTM approach discussed in Section \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata). The main output of interest are the types of topics identified by the model, and the prevalence of each topic on of each day of parliamentary discussion.

The remainder of the results refer to a topic model that had 80 distinct topics defined. The choice of 80 topics was made as a trade-off between the standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the topics to be tractable for our analysis model. The diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).

Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics. The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade. Note that some topics seem to somewhat overlap with their content: for instance, topics 4, 26, 28, 30 and 66 all relate to war and conflict.

@@

Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Australian House of Representatives between 1901 and 2017. It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time. The highlighted topics are those related to war and conflict.

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.png")
```

@@

We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament. As discussion in Section \@ref(analysismodelexplanation), the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events.

There are several outputs of interest from this modelling stage. For example, the model provides estimates of topic prevalence by each sitting period. This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability. For instance, examining Topics 12, 17, 22 and 23, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the first Gulf War, and the war in Afghanistan and the second Gulf War (Figure \@ref(fig:wartopicsgraph)).

@@

One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time. Political events are those related to a change of government or an election. As Australia has a parliamentary system, it is possible for the government to change without an election. We define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done. If a person was prime minister more than once then these are considered separately.

As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level effect for each government, $\alpha_g$ and each election, $\alpha_e$. We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals based on posterior samples of these respective mean effects. When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.

We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults). These tables focus on elections and governments that were different to the ones that preceded them.

@@

governments_results %>%
  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor, and neighbours") %>%
  kable_styling(font_size = 10)

@@

In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate differences between governments and elections, respectively. In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified. The error bars represent 95 per cent Bayesian credible intervals. The topics that we have focused on here are:
12, 17, 22, 23 which have to do with conflict, defence and security; 13 and 32 which have to do with commerce and trade; 24 and 33 which have to do with the budget, tax and spending; 29 which is to do with education and 39 which has to do with health.

@@

Although we do not explicitly include them in the model, the non-political events that we look for when considering periods of significant change are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision. The full list of events that we consider are detailed in Appendix \@ref(eventdetails). Note that we consider each chamber separately and future work could expand the model to better understand, and allow, for correlation between them.

We estimate sitting-period level-effects (essentially a mean for each topic by sitting period). The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days. This approach means that the model generates dates that are interesting without us having to specify interesting dates.

More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period. Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.

@@

# Discussion
Of the 36 different governments over this period, we find that 14 of them are significantly different to the government that preceded them. However, two of these results -- the significance of the Page  Government and the first Menzies Government -- are likely due to the short length of the Page Government and should be ignored, leaving only 12. The earliest of these are the Second and Third Fisher Governments, which were different to the Third Deakin Government and the Cook Government respectively. To a certain extent this is likely tied up with changes due to World War I.

The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor. The rest of the ones that are different are concentrated in the second half of our sample, with three of them being in the past twenty years. Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor. 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.

The second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government. The Chifley Government had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics. The sixteen-year length of the second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different.

There were six elections within the second Menzies Government. However we do not find that any of those elections was associated with a significant change in the topics discussed. In this sense it was a period of consistency, especially when compared with shorter-term Whitlam Government, or the longer-term Howard Government.

The Menzies Government was succeeded by the Holt Government in January 1966. This is an example where there was a change in government without an election, as the next election only happened in November 1966. We find that the Holt Government is significantly different to the Menzies Government. In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.

@@

The Whitlam government is interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974. Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.

The Howard Government is interesting because of the significant differences between elections. For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all apart from 2001 are actually significantly different at the 95 per cent level. Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.

@@

One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent. The results of this reduction in supervision are promising, but suggest specifics of our process need further refinement. For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively. It also appropriately identifies some of other key events that we were interested in. However there are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising. Further work is needed to improve this approach. For instance, our approach may not be appropriately considering step-changes.

# Conclusion
In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017. We download and parse PDFs of Hansard to create a new dataset of text. We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model. In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not. We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.

@@

In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model. Firstly, we are assuming that the effect of a particular government is constant across the whole period. In addition, we assume that the effect of elections is monotonically decreasing across days since election. In future work we will investigate different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.

The way that we identify unusual periods could also be improved. We defined sitting periods in a constant fashion across the whole dataset time frame, but the nature of how long parliaments sit for has most likely changed. In addition, more work needs to be done on how to identify outlying events. For example, it is not clear if an important event that occurs outside a sitting period would be identified. And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such specific days are not identified as significantly outlying.

Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model. However, this approach does not appropriately propagate uncertainty in topic distribution estimation. Future methodological work will focus on how to combine these two modelling steps by extending the STM approach into a more flexible framework.

@@

```{r asdf, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
knitr::include_graphics("../../figures/example_hansard_page.png")
```

@@

```{r differencesbyyear, echo=FALSE, fig.cap="Example Hansard page - 6 February 1902", out.width = '100%'}
knitr::include_graphics("../../figures/differences_by_year.pdf")
```

@@

## Example Hansard PDF to text record workflow {#hansardworkflow}
The exact scripts that we use are too long to provide here but are available on request. Instead here we provide shorterned scripts for the workflow to convert the PDFs to usable text datasets that may be a useful starting point for other researchers. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

@@

@@

governments %>% 
  kable(booktabs = T, caption = "Change in governments") %>%
  kable_styling(font_size = 10)

@@

elections %>% 
  filter(election == 1) %>% 
  select(year, electionDate, electionWinner) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 10)

```{r keyevents, echo = FALSE, results = 'asis'}

keyEvents %>% 
  kable(booktabs = T, caption = "Key events") %>%
  kable_styling(font_size = 10)

For background on the Premiers' Plan see @Copland1934.

For background on the Gruen tariff cut see @Gruen1975.

Add the graphs and procedures. **[TBD]**

>>>>

elections <-
  read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())

governments <-
  read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())

keyEvents <-
  read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())

significances <-
  read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())

top_words <-
  read_csv2(here::here("outputs/results-topic_models_and_gammas/top_words_80.csv"), col_types = cols()) %>% 
  rename(Topic = topic, Terms = terms)

@@

elections_results <-
  read_csv(here::here("outputs/results-analysis_model/results-elections.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Significant)

governments_results <-
  read_csv(here::here("outputs/results-analysis_model/results-governments.csv"), col_types = cols()) %>%
    filter(Significant %in% c("Yes")) %>%
    select(-Party,-`Died in Office`,-Significant)

key_events_results <-
  read_csv(here::here("outputs/results-analysis_model/results-outliers.csv"), col_types = cols()) %>%
    select(-Expected)

@@

The recent digitisation of the Canadian Hansard, @BeelenEtc2017, has allowed text analysis of Canadian parliament records. For instance, @RheaultCochran2018 examined ideology and party polarisation in Britain and Canada. A digitised version of the UK Hansard has been available for some time and there has been much text analysis of it. For instance, @Duthie2016 examined which politicians made supportive or aggressive statements toward other politicians and @PetersonSpirling2018 examined polarisation. One exciting aspect of research using the UK Hansard has been linking text records with other datasets. For instance, @SlapinKirklandLazzaroLeslie2018 linked votes and speeches to examine grandstanding within parties. Another exciting aspect is that as digitisation methods improve, increasingly older UK records can be analysed, for instance, @Dimitruk2018 considered the effect of estate bills on prorogations in seventeenth century England. In New Zealand, @Curran2018 modelled the topics discussed between 2003 and 2016, and @Graham2016 examined unparliamentary language between 1890 and 1950. And in the US, @GentzkowShapiroTaddy2018 examined congressional speech records from 1873 to 2016 to find that partisanship has risen in the past few decades.

@@

We use the official PDF release and the formatting of the Hansard records changes over time. We use scripts written in R, @R2018, to convert the PDFs into daily text records. An example of the workflow and some pseudo-code are provided in Appendix \@ref(hansardworkflow). Some error is introduced at this stage because many of the records are in a two-column format that need to be separated, and the PDF parsing is not always accurate especially for older records. An example of the latter issue is that 'the' is often parsed as 'thc'. These errors are corrected when they can be identified.

@@

## Topic modelling
We applied the CTM approach discussed in Appendix \@ref(correlatedtopicmodelsection) on the processed Hansard text database outlined in Section \@ref(hansarddata). The main output of interest are the types of topics identified by the model, and the prevalence of each topic for each day of parliamentary discussion.

Our results are for a topic model that had 80 distinct topics. With almost 15,000 days and 80 topics, the analysis model is being fit to more than a million observations. The choice of 80 topics was made as a trade-off between standard diagnostic tests that suggested a larger number of topics would be more appropriate, and the need for the analysis model to be tractable. Those diagnostic tests are detailed in Appendix \@ref(selecttopicnumber).

Table \@ref(tab:topwords) lists the top ten words associated with each of the 80 topics. The topics cover areas such as budgets, transport and infrastructure, war and conflict, health, education, agriculture, and trade. There are also some topics that appear to be about procedural or day-to-day, such as Topics 7 or 9. Note that, as expected, some topics seem to somewhat overlap with their content: for instance, Topics 4, 26, 28, 30 and 66 all relate to war and conflict.

@@

Figure \@ref(fig:exampletopics) illustrates the CTM output based on a sample from the Australian House of Representatives between 1901 and 2017. It shows how each day's parliamentary discussion can be apportioned to a topic and highlights how these proportions change over time. The highlighted topics are those related to war and conflict. As expected, the two chambers of the Australian Federal Parliament are fairly similar.

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with five topics highlighted", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example.png")

@@

### Main results

We are interested in considering the effect of various political and other events on what is talked about in the Australian Federal Parliament. As discussion in Section \@ref(analysismodelexplanation), the next stage of the modelling process takes the topic proportions estimated in the CTM approach, and models the association between these topic distributions and outside events. That is, the topic model outputs are inputs for our analysis model.

There are several outputs of interest from this modelling stage. For example, the model provides estimates of topic prevalence by each sitting period. This nicely illustrates how the topics change over time, as the daily estimates tend to be quite variable, but using periods defined by governments or elections tend not to provide enough variability. For instance, examining Topics 4, 26, 28, 30 and 66, which have to do with war and conflict illustrates Australia's involvement in World War I, World War II, the Korean War, the Vietnam War, the First Gulf War, the War in Afghanistan and the Second Gulf War (Figure \@ref(fig:wartopicsgraph)).

@@

One of the main goals of the analysis model is to see which political events are associated with changes in the prevalence of topics over time. Political events are those related to a change of government or an election. Note that as Australia has a parliamentary system it is possible for the government to change without an election as we define a government based on who is the prime minister, and do not distinguish between terms or cabinet composition as is sometimes done. If a person was prime minister more than once then these periods are considered independently.

As detailed in Section \@ref(analysismodelexplanation), the model estimates a mean level-effect for each government, $\alpha_g$ and each election, $\alpha_e$. We identify differences between neighbouring governments and between neighbouring elections based on calculating 95 per cent credible intervals from posterior samples of these respective mean effects. When these do not overlap we consider that the model finds a significant difference between either the neighbouring governments or elections.

We summarise our results in terms of governments in Table \@ref(tab:governmentsresults) and in terms of elections in Table \@ref(tab:electionsresults). These tables focus on elections and governments that were different to the ones that preceded them. Complete lists of elections and governments are available in Appendices \@ref(fulllistofelections) and \@ref(fulllistofgovernments).

@@

governments_results %>%
  kable(booktabs = T, caption = "Governments that were significantly different to their predecessor") %>%
  kable_styling(font_size = 10)

@@

In Figures \@ref(fig:mugov) and \@ref(fig:muelection) we focus on certain topics to illustrate significant differences between governments and elections, respectively. In the graphs, the points show the estimated value of $\alpha_g$ and $\alpha_e$, respectively, for each of the topics specified. The error bars represent 95 per cent Bayesian credible intervals. We have focused on Topics 4, 26, 28, 30 and 66 here which have to do with war and conflict.

@@

### Additional results

Once government and election effects have been taken into consideration, some days stand out compared with others in their sitting period. We do not explicitly include them in the model because of over-fitting and effect-type concerns, but we are interested to see if these can be explained by events that occured on or before that sitting day. For instance, we may expect that events of a historical magnitude, such as the 9/11 attacks would be the focus of an entire day's discussion, or that the sitting day when the Apology to the Stolen Generation was delivered, or some particular legislation introduced, would be different to others in that sitting period.

To do this we estimate sitting-period level-effects (essentially a mean for each topic by sitting period). The difference between this mean distribution and a particular day's topic distribution defines a measure that can be thought of as essentially a residual which allows us to identify outlying days. This approach means that the model generates dates that are interesting without us having to specify interesting dates. More specifically, we define a day to be 'outlying' or 'different-to-expected' if the topic distribution on that particular day is more than three standard deviations different to the mean topic distribution for the relevant sitting period. Table \@ref(tab:keyeventsresultstable) summarises the days where parliamentary discussion was significantly different from the rest prevailing in that week.

@@

# Discussion
Of the 36 governments over this period, we find that 20 of them are significantly different to the government that preceded them. However, four of these results -- the significance of the Page Government, the First Menzies Government, the Chifley Government and the Abbott Government -- are likely due to the short length of either the government or its predecessor and should be ignored, leaving only 16. The earliest of these is the First Fisher Government, the Cook Government and the Third Fisher Government, which were different to the Second Deakin Government, the Second Fisher Government, and the Cook Government, respectively. To a certain extent this is likely due to changes due to World War I.

The Second Menzies Government, starting in 1949, is the next government that is significantly different to a predecessor. The rest of the governments that are different are concentrated in the second half of our sample, with three of them being in the past twenty years. Similarly, of the 45 general elections that have been held we find that 14 of them define periods that were significantly different to their immediate predecessor. 1974, 1980, 1990, 1998, 2004, and 2007 stand out as elections where the government did not change, but the model suggests there was considerable change in the topics discussed in parliament.

The Second Menzies Government was associated with a variety of changes compared with the preceding Chifley Government. The Chifley Government had governed through the end of World War II and the difficult economic times that followed. There was also a large increase in the number of seats in the House of Representatives at the 1949 election. Many new politicians entered parliament and this changed representation may also have been partly to do with the changed distribution of discussion topics. The sixteen-year length of the Second Menzies Government, and better economic conditions over this time make it understandable why parliamentary discussion would have been different. There were six elections within the Second Menzies Government. Three toward the middle of that government were associated with significant changes in the topics discussed.

The Menzies Government was succeeded by the Holt Government in January 1966. This is an example where there was a change in government without an election, as the next election only happened in November 1966. We find that the Holt Government is different to the Menzies Government. In Figures \@ref(fig:muelectionall) we compare the topics during the final term of the Menzies Government with the topics of the Holt Government.

@@

The Whitlam government is especially interesting as we find a difference in the topics after it was first elected in December 1972, compared with its second election win in May 1974. Figure \@ref(fig:muelectionall) compares the topics that are significant in the first Whitlam term and then compares them to those in the second Whitlam government.

The Howard Government is also interesting because of the significant differences between elections. For instance, each of the election periods is associated with fairly substantial differences compared with the preceding election periods, and all are actually significantly different at the 95 per cent level. Figure \@ref(fig:muelectionall) compares the topics that are significant in the different Howard terms.

@@

One advantage of our analysis model, compared with using the STM approach is that we can create a measure that is equivalent to testing for outliers in a model where the underlying variables were not latent. The results of this reduction in supervision are promising, but suggest the specifics of our process may need further refinement. For instance, our approach appropriately identifies the sitting day that first follows 11 September 2001 and 12 October 2002, which were the dates of the 9/11 Attacks and Bali Bombings respectively. It also appropriately identifies some of other key events in Australian history, such as X and Y. There are many dates that we would have expected to be identified that were not, and similarly some of the dates that were identified are surprising. When we dig into this we find that some of them, such as X and Y, are associated with significant legislation. Further work is needed to improve this approach. For instance, our approach may not be appropriately considering step-changes.

# Summary, weaknesses and future work
In this paper we consider what was said in the Australian Federal Parliament between 1901 and 2017. We download and parse PDFs of Hansard to create a new dataset of text. We use a correlated topic model to group the parliamentary discussion into topics to reduce the dimensionality, and then analyse the effect of various events on the distribution of these topics using a Bayesian hierarchical Dirichlet model. In general we find that changes in government change the distribution of topics discussed in parliament, but that most elections did not. We find that significant events such as 9/11 and the Bali Bombings had a substantial effect, but that with certain exceptions, economic events did not.

@@

In terms of the analysis model which relates the topic distributions with events, there are several limitations to the model. Firstly, we are assuming that the effect of a particular government is constant across the whole period. In addition, we assume that the effect of elections is monotonically decreasing across days since election. Future work could consider different functional forms on both of these effects, and in particular try to allow for elections to have a 'lead-up' effect.

The way that we identify unusual periods could also be improved. We defined sitting periods in a constant fashion across the whole dataset time frame, but how long the stretches are that parliament sits for has changed over time. In addition, more work needs to be done on how to identify outlying events. For instance, the extent to which an important event that occurs outside a sitting period can be identified has a great deal of uncertainty. And if an event happens in the middle of an sitting period, it may have a large effect on the overall mean, such that specific days are not identified as significantly outlying.

Finally, the current modelling and analysis set-up is a two-stage process: we take the output of a topic model, and use this as the input to a second model. However, this approach does not appropriately propagate uncertainty in topic distribution estimation. Future methodological work could consider how to combine these two modelling steps by extending the STM approach into a more flexible framework.

@@

```{r hansardexamplepage, echo=FALSE, fig.cap="Example Hansard page -- 6 February 1902", out.width = '65%', fig.align='center'}
knitr::include_graphics("../../figures/example_hansard_page.png")
```

@@

```{r differencesbyyear, echo=FALSE, fig.cap="Differences by year between the number of sitting days and our number of PDFs", out.width = '100%'}
knitr::include_graphics("../../figures/differences_by_year.pdf")
```

@@

## Example Hansard PDF to text record workflow {#hansardworkflow}
The exact scripts that we use are too long to provide here but are available on request. Instead here we provide shorterned pseudo-code that summarises the workflow to convert the PDFs to usable text datasets and may be a useful starting point for other researchers. The scripts are primarily based on: the \texttt{PDFtools} R package of @Ooms2018pdftools; the \texttt{tidyverse} R package of @Wickham2017; the \texttt{tm} R package of @FeinererHornik2018; the \texttt{lubridate} R package of @GrolemundWickham2011; the \texttt{tidytext} R package of @SilgeRobinson2016; and the \texttt{stringi} R package of @Gagolewski2018. The functions of those packages are augmented by: the \texttt{furrr} R package of @VaughanDancho2018; and the \texttt{tictoc} R package of @Izrailev2014. The \texttt{hunspell} R package of @Ooms2017 is used to help find spelling issues; and the \texttt{quanteda} R package of @Benoit2018 is used to compound multiword expressions.

@@

## List of Elections {#fulllistofelections}

elections %>% 
  filter(election == 1) %>% 
  select(year, electionDate, electionWinner) %>% 
  kable("latex", booktabs = T, caption = "Elections") %>%
  kable_styling(font_size = 8)

## List of Governments {#fulllistofgovernments}

@@

governments %>% 
  kable(booktabs = T, caption = "Change in governments") %>%
  kable_styling(font_size = 8)

@@

<!-- ## List of Other Events {#othereventsdetails} -->

<!-- ```{r keyevents, echo = FALSE, results = 'asis'} -->

<!-- keyEvents %>%  -->
<!--   kable(booktabs = T, caption = "Key events") %>% -->
<!--   kable_styling(font_size = 8) -->

<!-- ``` -->

<!-- For background on the Premiers' Plan see @Copland1934. -->

<!-- For background on the Gruen tariff cut see @Gruen1975. -->
